% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\begin{frame}

404050 VU Empirical Economics: Impact Evaluation
\end{frame}

\begin{frame}{Organizational Information}
\phantomsection\label{organizational-information}
\begin{block}{Who we are}
\phantomsection\label{who-we-are}
\begin{block}{Lecturer:}
\phantomsection\label{lecturer}
Univ.-Prof.~Andreas Steinmayr, Ph.D.\\
\href{mailto:andreas.steinmayr@uibk.ac.at}{\nolinkurl{andreas.steinmayr@uibk.ac.at}}\\
\href{http://www.andreassteinmayr.net}{www.andreassteinmayr.net}
\end{block}

\begin{block}{Teaching Assistant:}
\phantomsection\label{teaching-assistant}
Elias Balayan
\href{mailto:el.balayan@uibk.ac.at}{\nolinkurl{el.balayan@uibk.ac.at}}
\end{block}
\end{block}
\end{frame}

\begin{frame}{Organizational Information}
\phantomsection\label{organizational-information-1}
\begin{block}{How to contact us}
\phantomsection\label{how-to-contact-us}
\begin{itemize}
\tightlist
\item
  Please email me or Elias Balayan to schedule an appointment.
\item
  In between the sessions, you can also use the OLAT forum to ask
  questions. The questions will be public so that others can benefit
  from the answers as well.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Organizational Information}
\phantomsection\label{organizational-information-2}
\begin{block}{Timetable}
\phantomsection\label{timetable}
\begin{itemize}
\tightlist
\item
  \textbf{Lectures:}\\
  Wed. 02.10. - 04.12.

  \begin{itemize}
  \tightlist
  \item
    \textbf{Exam:}\\
    Wed. 11.12.
  \end{itemize}
\item
  \textbf{Work on empirical projects:}\\
  December - January
\item
  \textbf{Seminar day:}\\
  Wed. 31.01.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Class material}
\phantomsection\label{class-material}
All material will be uploaded to or linked on the OLAT page of the
course

\begin{itemize}
\tightlist
\item
  Lecture slides
\item
  Textbooks
\item
  Research articles
\item
  Data for empirical projects
\end{itemize}
\end{frame}

\begin{frame}{Textbooks}
\phantomsection\label{textbooks}
\begin{block}{Central textbooks:}
\phantomsection\label{central-textbooks}
\begin{itemize}
\tightlist
\item
  Gertler, P. J. et al.~(2016). \emph{Impact Evaluation in Practice}.
  2nd Edition, World Bank Publications.\\
  \href{http://www.worldbank.org/ieinpractice}{www.worldbank.org/ieinpractice}
\item
  Huntington-Klein, N. (2021). \emph{The Effect: An Introduction to
  Research Design and Causality}. CRC Press.
  \url{https://theeffectbook.net/}
\end{itemize}
\end{block}

\begin{block}{Supplementary econometrics textbooks:}
\phantomsection\label{supplementary-econometrics-textbooks}
\begin{itemize}
\tightlist
\item
  Cunningham, S. (2021). \emph{Causal Inference: The Mixtape}. New
  Haven: Yale University Press.\\
  \url{https://mixtape.scunning.com/}
\item
  Angrist J. and J-S Pischke (2014). \emph{Mastering Metrics}, Princeton
  University Press.
\item
  Angrist J. and J-S Pischke (2009). \emph{Mostly Harmless
  Econometrics}, Princeton University Press.
\end{itemize}

In addition, we will discuss some research articles that I will make
available to you.
\end{block}
\end{frame}

\begin{frame}{Examination}
\phantomsection\label{examination}
\begin{itemize}
\tightlist
\item
  \textbf{Own empirical project} (in groups of 2 to 3 students) (40\%)

  \begin{itemize}
  \tightlist
  \item
    Presentation during seminar day
  \item
    Report
  \item
    More details on the empirical project in the coming weeks
  \end{itemize}
\item
  \textbf{Short-exams} (15\%)

  \begin{itemize}
  \tightlist
  \item
    Three unannounced short exams at the beginning of the respective
    session
  \item
    On the topic of the required reading for the session
  \end{itemize}
\item
  \textbf{Final exam} (35\%)
\item
  \textbf{Participation in class} (10\%)
\end{itemize}
\end{frame}

\begin{frame}{What is expected of you}
\phantomsection\label{what-is-expected-of-you}
\begin{itemize}
\tightlist
\item
  Active participation throughout the course
\item
  Read the respective sections of the textbook \& assigned research
  papers before class
\item
  Theoretical and practical knowledge of econometric methods

  \begin{itemize}
  \tightlist
  \item
    This is not an introductory econometrics class
  \end{itemize}
\item
  Basic knowledge in working with R

  \begin{itemize}
  \tightlist
  \item
    For a refresher and more advanced materials, look at Prof.~Zeileis'
    \href{https://www.zeileis.org/teaching/R-Intro/}{R-Introduction} and
    \href{https://www.zeileis.org/teaching/R-Programming/}{R-Programming}
    guides.
  \end{itemize}
\item
  Apply the knowledge you gain in this course
\end{itemize}
\end{frame}

\end{document}
