\documentclass[
  25pt,         % default font size: 17pt, 20pt(default), 25pt, 30pt
  a4paper,
  landscape,
  Screen4to3,
% headrule,
  footrule ]{foils}

\usepackage[%
    a4paper,%
    bookmarks=false,%
    colorlinks=false,%
    pdftitle={404050 VU/3 VU Empirical Economics: Impact Evaluation, Fall 2023},%
    pdfauthor={Andreas Steinmayr}%
    ]{hyperref}


\usepackage[OT1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{hyperref}
\usepackage{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{hyperref}
\usepackage{tikz}



\input{jo-math}

\newcommand{\Perp}{\perp \! \! \! \perp}

%================================================================
% Global macros
%================================================================
 \MyLogo{Andreas Steinmayr, 404050 VU/3 VU Empirical Economics: Impact Evaluation, Fall 2023}
 \rightfooter{\thepage}

 \newcommand{\sectiontitle}{}

%================================================================
% Toggle lecture / print version
%================================================================

\newboolean{lecture}

\setboolean{lecture}{true}

\ifthenelse{\boolean{lecture}}{%
  \usepackage[
      display,        % enable dynamic features for presentations
      whitebackground % enable blue-on-white colors for presentations
  ]{texpower}
  \newcommand{\textclr}{\usecolorset{whitebackground}}
  \newcommand{\lecture}[1]{#1}
  \newcommand{\lecturep}[1]{#1}
  }
  {
  \usepackage{texpower}
  \newcommand{\textclr}{\color{black}}
  \renewcommand{\pause}{}
  \newcommand{\lecture}[1]{}
  \newcommand{\lecturep}[1]{\phantom{#1}}
  }

\newcommand{\wait}{\pause \vspace{-1mm}}

\newcommand{\xx}{\item[{\small $\bullet$}]}

\newcommand{\definition}{{\bf Definition:}\;}
\newcommand{\result}{{\bf Result:}\;}
\newcommand{\namedresult}[1]{{\bf Result~(#1):}\;}

 \addtolength{\textheight}{\headheight +\headsep +\footskip +.3in}
 \setlength{\headheight}{0pt} \setlength{\headsep}{0pt}
 \setlength{\footskip}{0pt} \setlength{\foilheadskip}{-.2in}


%================================================================
% Colors
%================================================================

\definecolor{red}{rgb}{1,0,0}
\definecolor{green}{rgb}{0,1,0}

\boxedsteps % turn on boxedsteps


%================================================================
\begin{document}

\setlength{\parindent}{0pt}


%================================================================
\foilhead{404050 VU Empirical Economics: Impact Evaluation}

\thispagestyle{empty}

\begin{center}

Andreas Steinmayr \\ 

\bigskip \bigskip \bigskip

Department of Economics \\
University of Innsbruck \bigskip

Fall 2023

\end{center}


%================================================================

%\ifthenelse{\boolean{lecture}}{\input{adveco_110204.tex}}{}

\setcounter{page}{0}

%================================================================
\foilhead{Organizational information}

\textbf{Who we are}

\textbf{Lecturer} \\
Univ.-Prof. Andreas Steinmayr, Ph.D. \\ 
\href{mailto:andreas.steinmayr@uibk.ac.at}{andreas.steinmayr@uibk.ac.at} \\ \url{www.andreassteinmayr.net}
\bigskip

\textbf{Teaching Assistant} \\
Sebastian Kupek \\
\href{mailto:sebastian.kupek@uibk.ac.at}{sebastian.kupek@uibk.ac.at}


%================================================================
\foilhead{Organizational information}

\textbf{How to contact us}

\bi
   \x Please email me or Sebastian Kupek to schedule an appointment.
   \x In between the sessions, you can also use the OLAT forum to ask questions. The questions will be public so that others can benefit from the answers as well.
\ei

%================================================================
\foilhead{Organizational information}

\textbf{Timetable}

	\begin{itemize}
		\vsm\item Wed. 04.10. - 07.12. -- \textit{Lectures}
    \begin{itemize}
	          \item Wed. 13.12. -- \textit{Exam}
    \end{itemize}
    \vsm\item December - January -- \textit{Work on empirical projects}    
		\vsm\item Wed. 26.01. -- \textit{Seminar day}
	\end{itemize}



%================================================================
\foilhead{Organizational information}

\textbf{Material}

\bi

  \x All material will be uploaded or linked to OLAT
  \bi
    \xx Lecture slides
    \xx Textbooks (if pdf available)
    \xx Research articles
    \xx Data for empirical projects
  \ei
\ei


%================================================================

\foilhead{Textbooks}

\begin{small}

\bi
\x \textbf{Central textbook:} \vsm
\bi
\xx Gertler, P. J. et al. (2016). \emph{Impact Evaluation in Practice.} 2nd Edition, World Bank Publications. \url{www.worldbank.org/ieinpractice}
\medskip
\xx Cunningham, S. (2021). \emph{Causal Inference: The Mixtape.} New Haven: Yale University Press. \url{https://mixtape.scunning.com/}

\ei


 \x \textbf{Supplementary econometrics textbooks:} \vsm
\bi
 \xx Angrist J. and J-S Pischke (2014), \emph{Mastering Metrics\/}, Princeton University Press.
 \xx Angrist J. and J-S Pischke (2009), \emph{Mostly Harmless Econometrics\/}, Princeton University Press.
\ei
 \x In addition, we will discuss some research articles that I will make available to you.
\ei
\end{small}

%================================================================
\foilhead{Examination}
\bi 
\x Own empirical project (in groups of 2 to 3 students) (50\%)
\bi
  \xx Presentation during seminar day
  \xx Report
  \xx More details on the empirical project in the coming weeks
\ei
\x Final exam (40\%)
\x Participation in class (10\%)
\ei

%================================================================
\foilhead{What is expected of you}
\bi
\x Active participation throughout the course
\x Read the respective sections of the textbook \& assigned research papers before class
\x Theoretical and practical knowledge of econometric methods
\bi
\xx This is not an introductory econometrics class
\ei
\x Apply the knowledge you gain in this course
\ei

%================================================================
\end{document}
